---
title: 'section 10.5'
author: "Yuehan Xiao"
date: "2/20/2018"
output: html_document
---

1. 
```{r}
library(tibble)
print(mtcars)
class(mtcars)
is.tibble(mtcars)
```
mtcars is not a tibble as indicated by the code. 
Also, data.frame will show all the data on the console compare to tibble, which only shows the first 10 rows of data. 

2. 
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]

df1 <-tibble(abc = 1, xyz = "a")
df1$x
df1[, "xyz"]
df1[, c("abc", "xyz")]

```
 For tibble, if you want to pull out a single varible, you must type the whole name for the variable. However, for data.frame, you can do partial matching. 
 
 When we type "[ ]""the data frame will returns a factor but the tibble returns a data frame.  
 
 

3. 
We use tibble$name, or tibble[["name"]] to extract the variable

4. 
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)

annoying$`1`

ggplot(data = annoying) + 
  geom_point(mapping = aes(x = `1`, y = `2`))

annoying <- annoying %>% mutate(`3` = `2`/`1`)

annoying %>%
  rename(one = `1`,
         two = `2`,
         three = `3`)
```

5. 
```{r}
tibble::enframe()
```
it converts named atomic vectors or lists to two-column data frames. 

6. 
```{r}
library(fivethirtyeight)
options(tibble.max_extra_cols = 5)

police_killings
```

